---
title: "Kijiji Used Cars"
output: 
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bg: "#d9d9d9" # black
      fg: "#101010" # light grey d9d9d9
      primary: "#ED79F9" # pink
      navbar-bg: "#3ADAC6" # teal
      font: "Lato"
    orientation: columns
    vertical_layout: fill
runtime: shiny
---



```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(shiny)
library(tidytext)
library(ggtext)
library(DT)


penguins= palmerpenguins::penguins
starwars = starwars

df = read_csv2('kijiji_cars_v2.csv')
```

```{r}
# glimpse(df)
# df$location = as.factor(df$location)
```



Project Details
=========================================

#### Kijiji Used Cars

This project was a project to find data on used cars from the website kijiji.ca, where data was scraped on October 15, 2021.
Data from webscraping was cleaned and formatted to be used for data analysis. This project was not an extensive web scraping exercise, but to demonstrate the multiple step process in a data science project, and to end up with a dashboard to share with stakeholders.


> The data pipeline involves finding data, getting the data, cleaning the data or also known as data wrangling, visualizing the data and to save the cleaned data into a file for further use.

**Note**: *The website data on used cars is from the province of Alberta. No detailed parameters were made, resulting in page 1 only data with 90 rows of data.*

# Row
----------
### Used Cars in Alberta  

The barplot on the right shows the number of used cars for sale advertised on kijiji.ca on October 15, 2021 by location. 

The city of Calgary clearly has the most posts regarding selling a car and or vehicle parts.

### Chart 0 
-----------------------------------------

```{r}


df %>% 
  select(title, location) %>% 
  group_by(location) %>% 
  count(location, sort = T) %>% 
  ggplot( aes(x= n, y= reorder(location, n) ))+
  geom_col(fill= "#3ADAC6")+
  labs(title = "Kijiji Used Cars by Location in Alberta",
       y="",
       x= "Count")+
  theme(
    plot.title = element_markdown(face = 'bold',
                                  size = 15,
                                  color = '#33b093'),
    plot.subtitle = element_markdown(size = 12),
    axis.text.y = element_markdown(face = 'bold',
                                   size= 12),
    axis.text.x = element_markdown(size = 12)
  )

```

***
Comments on this data plot

---------






Plot 1
============
***
#### Text Analysis

After the data was scraped and cleaned from the website, the column for description from each post made was tokenized.
This section has the full paragraph description what the person is selling.

One of the descriptions gathered was:

> "Fully loaded V6 platinum Nissan Murano in excellent condition. No accident, clean vehicle with up to date service record from Nissan dealership. Pearl white colour, beige interior, heated front and ... Automatic | 38,000 km" 


The library **TidyText** was used to vectorized each word, and then the *stop_words* library was used to strip away the paragraph's sentences to word form. Some of the data that had high counts included street addresses, so these were removed along with the condition word counts greater than 10 be returned. 


-------
```{r fig.height=5, fig.width=9}
library(tidytext)

text_df = tibble(line=1:90, text= df$description)

info_txt_df = tibble(line=1:90, text= df$info)

text_df = text_df %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words)

info_txt_df =info_txt_df %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words)


text_df %>% 
  count(word, sort = T) %>% 
  filter(n > 10,
         word != c('15799','116ave')) %>% 
  mutate(word = reorder(word, n)) %>% 
  ggplot( aes(x= n, y= word))+
  geom_col(fill="#3ADAC6")+
  labs(title = "Used Cars Word Counts in kijiji Descriptions", 
       subtitle = "Data Webscraped on Oct. 15, 2021",
       y= "",
       x="Count")+
  theme(
    plot.title = element_text(size = 14, face = 'bold'),
    axis.text.y = element_text(face = 'bold', size=11)
  )
```



The top words in the descriptions are `vehicle`, `km` as to indicate how many kilometers are the vehicle has been used, and `automatic` for the type of vehicle transmission. It also appears the second group of common words when selling a vehicle is to have `condition`, `luxury` status and the state of the `tires`. 

--------------



<!-- *** -->
<!-- comments go here -->

<!-- # panel {.sidebar} -->


Plot 2
========
***
#### Text Analysis 2

This data is from the information section of the post, where some of the information is more in depth than the brevity of description section. For example, the same user from the description has more details on their Nissan vehicle.


> "$37,900.00 Nissan Murano Platinum Calgary 13/10/2021
Fully loaded V6 platinum Nissan Murano in excellent condition. No accident, clean vehicle with up to date service record from Nissan dealership. Pearl white colour, beige interior, heated front and ... Automatic | 38,000 km" 


Notice that the key words are `vehicle`, `automatic` and `km` appear here as along with the condition of the vehicle.


```{r fig.height=6, fig.width=9}

digits = "[[:digit:]]"
info_txt_df$word = str_remove_all(info_txt_df$word, digits )  
punct = "[[:punct:]]"
info_txt_df$word = str_remove_all(info_txt_df$word, punct )  
blanks = "[[:blank:]]"
info_txt_df$word = str_remove_all(info_txt_df$word, blanks ) 

ctrl_chars = "[[:cntrl:]]" 
info_txt_df$word = str_remove_all(info_txt_df$word, c("","ago")) 
info_txt_df$word = str_remove_all(info_txt_df$word, "\\s+" )

info_txt_df$word = str_remove_all(info_txt_df$word, c("hours") )

info_txt_df$word = str_remove_all(info_txt_df$word, c("ago") )
info_txt_df$word = str_replace(info_txt_df$word ,"cagary", "calgary" )


info_txt_df %>% 
  count(word, sort = T) %>% 
  drop_na(word) %>%
  filter(n < 80 & n > 10
         ) %>%
  mutate(word = reorder(word, n)) %>% 
  ggplot( aes(x= n, y= word))+
  geom_col(fill="#3ADAC6")+
  labs(title = "Used Cars on Kijiji.ca - Word Counts (from info section)", 
       subtitle = "Data Webscraped on Oct. 15, 2021",
       y= "",
       x="Count")+
  theme(
    plot.title = element_text(size = 14, face = 'bold'),
    axis.text.y = element_text(face = 'bold', size=11)
  )

```



## Header

String manipulation was used to detect, extract, and remove words from the data. Word punctuation, blank spaces and control characters were removed.




Plot 3
==========
***
#### Cars by Year

This section deals with extracting years from the information, title, and description columns. The *stringr* library was used to pull numerical digits from the string data. 

```{r fig.height=4, fig.width=8}
df %>% 
  count(car_year, sort = T) %>% 
  drop_na() %>% 
  unique() %>% 
  ggplot( aes(x= n, y= reorder(car_year, n)) )+
  geom_col(fill="#3ADAC6")+
  labs(title = "Used Cars on Kijiji.ca - Car Year Counts", 
       subtitle = "Data Webscraped on Oct. 15, 2021",
       y= "",
       x="Count")+
  theme(
    plot.title = element_text(size = 14, face = 'bold'),
    axis.text.y = element_text(face = 'bold', size=11)
  )

```

***
The year 2016 is missing from the plot, but is captured in the data, occurring once for a Toyota Tacoma.



Plot 4
==========
***
#### Cars by Type

The data scraped from kijiji was not specified and was merely the first page for used cars with no parameters modified. This data was made by doing a detection of specific strings, and creating a dataframe for the counts for car brands inside the title column.

The car brands most occurring in the dataset is `Ford`s and `HONDA`s, as 
Ford F150 is common along with Honda Civics. The `BMW` car brand is also counted. With further inspection, the BMW data has 1 car for sale, else it is related to floor mats and not the car itself.




```{r fig.height=4, fig.width=8}
car_type_counts = tribble(
  ~type, ~count,
  'Ford',12,
  'Toyota',2,
  'BMW',8,
  'Chevrolet',2,
  'Mazda',4,
  'HONDA',8,
  'Hyundai',4,
  'Subaru',4,
  'Jeep',2,
  'Lincoln',2,
  'Nissan',2
  
)

ggplot(car_type_counts,
       aes(x= count, y= reorder(type, count)))+
  geom_col(fill="#3ADAC6")+
  scale_x_continuous(breaks = c(2,4,6,8,10,12))+
  labs(title = "Count of Used Car Brands on kijiji ",
       y="Car Brands")+
  theme(
    plot.title = element_text(size = 14, face = 'bold'),
    axis.text.y = element_text(face = 'bold', size=11)
  )
```














<!-- luctus molestie nulla. Morbi molestie tortor sem, interdum molestie felis ornare at. In imperdiet faucibus dapibus. Phasellus interdum, lectus a pretium sagittis, sapien sem auctor odio, eu efficitur augue elit rutrum nisl. -->

<!-- ### Data Analysis  2 -->
<!-- ------------ -->

<!-- Aliquam sed volutpat nulla. Aliquam id dui orci. Aliquam pharetra fermentum diam vitae aliquam. Duis tellus leo, malesuada condimentum libero et, luctus molestie nulla. Morbi molestie tortor sem, interdum molestie felis ornare at. In imperdiet faucibus dapibus. Phasellus interdum, lectus a pretium sagittis, sapien sem auctor odio, eu efficitur augue elit rutrum nisl. Ut ut posuere urna. Donec sit amet diam eget ex lacinia commodo quis eu leo. -->
